A Hitchhiker's Guide to Reproducible Research" # replace with something serious

### 2021-05-10 manuscript.Rmd
recomend to put each sentence on a newline closes #50
some spelling errors and clarifications

If these commands detect that a given software requirement is not installed or set up properly, you will get a message with detailed instructions (tailored to your operating system) on how to set up your computer.
Please make sure that all three commands pass before you continue with the tutorial.
This process is only required once per computer and does not need to be repeated per project.

@@

<!-- researcher should begin early to enjoy most benefits -->
Reproducibility is invaluable for effective collaboration---including with your "past self".
While you might be tempted to consider reproducibility only when you about to finish a project, upfront investments pay off through your increased productivity.
Therefore, we suggest starting early, ideally from the moment you decide to pursue a project to incorporate tools to help you achieve reproducibility gradually.
The first step towards reproducibility is to bundle all required files in one folder.
This way, you never lose anything, and you can easily share the files without missing anything.
<!-- Hands-on: Introducing RProjects-->
RStudio's _R Projects_ facilitate this concept of a project folder.
To create one, click on:

@@

And GitHub can show you what has changed, like in Figure \@ref(fig:idea-change).
GitHub is, in its essence, a web interface to Git, and you may learn more about how to use it under the section on [GitHub].

@@

You can also manually edit the `Dockerfile` by amending the file `.repro/Dockerfile_manuel` to install software beyond R packages.
Remember to run `repro::automate()` after you made edits to `.repro/Dockerfile_manuel`.
We recomend @wiebelsLeveragingContainersReproducible2021 as a starting point for researcher who want to better understand how they can employ Docker for research.

>>>>

If any of these commands find that a given software requirement is not installed or set up properly, you will get a message with detailed instructions (tailored to your operating system) on how to set up your computer.
Please make sure that all three commands pass before you continue with the tutorial.
This process is only required once per computer and does not need to be repeated for each project.

@@

<!-- researcher should begin early to enjoy most benefits -->
Reproducibility is invaluable for effective collaboration---including with your "past self".
While you might be tempted to consider reproducibility only when you about to finish a project, upfront investments pay off through your increased productivity.
Therefore, we suggest starting early, ideally from the moment you decide to pursue a project to incorporate tools to help you achieve reproducibility gradually.
The first step towards reproducibility is to bundle all required files in one folder.
This way, you never lose anything, and you can easily share the files without missing anything.
<!-- Hands-on: Introducing RProjects-->
RStudio's _R Projects_ facilitate this concept of a project folder. The `repro` package offers an R Studio template, which sets up a file structure that follows best practices and conventions.<!--AP this is from your thesis - can you please add citations as to which practices and conventions these are?-->
To create one, click on:

@@

And GitHub can show you what has changed, like in Figure \@ref(fig:idea-change).
This detection of what has changed works on a line-by-line basis.
We recommend therefore to keep each sentence in a Markdown on its own line to generate clean difference views.
GitHub is, in its essence, a web interface to Git, and you may learn more about how to use it under the section on [GitHub].

@@

You can also manually edit the `Dockerfile` by amending the file `.repro/Dockerfile_manuel` to install software beyond R packages.
Remember to run `repro::automate()` after you made edits to `.repro/Dockerfile_manuel`.
We recommend @wiebelsLeveragingContainersReproducible2021 as a starting point for researcher who want to better understand how they can employ Docker for research.
